Capstone Movielens Report

### 2025-12-16 reports/capstone-movielens.site/02.8-0.UMGYDE-model.Rmd
Mino fix for the previous commit.

  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to to select the best value of the *tuning parameter* from the given sequence of the *parameter values* (passed in the [param_values](#func.tune.model_param.args.param_values) argument).

>>>>

  - [tune.model_param](#func.tune.model_param) (described in the *Common Helper Functions /* [Model Tuning Utils](#appndx_a.CHF.model_tuning_utils) section) to select the best value of the *tuning parameter* from the given sequence of the *parameter values* (passed in the [param_values](#func.tune.model_param.args.param_values) argument).
